# Data exploration

## Read data

First, we install and load the R packages `here` and `runjags` if needed. Also, we load the `here` package.

```{r install-pkg, eval=FALSE}
install.packages("here")
install.packages("runjags") 
```

```{r}
library(here) # Load here
```

Second, we read in the RN4CAST data. (Adjust the file path if you need to). The original file had 2 extra (empty) columns. We deleted these beforehand.

```{r read-data}
data_path <- "../BurnoutPA.txt"
RN4CAST <- read.delim(here(data_path))
```

We then format the column types, based on the information provided in the assignment. 
<!--- clean out commented text lines in code block --->

```{r load, echo=FALSE}
library(readr)
# column_names <- c(
#     "hosp",
#     "unit",
#     "tech",
#     "teach",
#     "beds",
#     "surgical_unit",
#     "work_environment_index",
#     "experience",
#     "fulltime",
#     "personal_accomplishment"
# )
RN4CAST <-
    read_table(
        data_path,
        col_names = TRUE,
        # col_names = column_names,
        col_types = cols(
            col_integer(),
            col_integer(),
            col_factor(),
            col_factor(),
            col_integer(),
            col_factor(),
            col_double(),
            col_double(),
            col_factor(),
            col_integer()
        )
    )
```

RN4NCAST has 1118 complete observations of the following variables:

**Nurse level**

-   `expe`: experience (years of employment)
-   `full`: full time nurse indicator (0/1)
-   `pa`: reduced personal accomplishment (PA) dimension of burnout
    (higher values indicate a higher burnout / reduction in PA)

**Nursing unit level**

-   `unit`: a nursing unit identifier
-   `unitsur`: surgical unit indicator (0/1)
-   `we`: work environment index (higher values indicate a more positive
    work environment)

**Hospital level**

-   `hosp`: a hospital identifier
-   `tech`: technical hospital indicator (0/1)
-   `teach`: teaching/university hospital indicator (0/1)
-   `beds`: number of beds

## Univariate

Provide univariate summary statistics of all variables, as well as histograms of pa.

```{r summary}
summary(RN4CAST)
```

```{r hist, out.width="50%", fig.align='center'}
hist(
  RN4CAST$pa, 
  main = "Histogram of Reduced Personal Accomplishment Score",
  xlab = "Reduced Personal Accomplishment Score"
  )
```

The distribution of PA is positively skewed, with only very few high values.
