# Data modelling

## Set up 

First, we install and load the R packages `here` and `runjags`.

```{r load-pkg, message = FALSE}
library(parallel)
library(runjags) # Load runjags
```

```{r}
# set.seed(12345)
```

We have the following variables:

**Nurse level**

- `expe`: experience (years of employment)
- `full`: full time nurse indicator (0/1)
- `pa`: reduced personal accomplishment (PA) dimension of burnout (higher values indicate a higher burnout / reduction in PA)

**Nursing unit level**

- `unit`: a nursing unit identifier
- `unitsur`: surgical unit indicator (0/1)
- `we`: work environment index (higher values indicate a more positive work environment)

**Hospital level**

- `hosp`: a hospital identifier
- `tech`: technical hospital indicator (0/1)
- `teach`: teaching/university hospital indicator (0/1)
- `beds`: number of beds

```{r hist, out.width="50%", fig.align='center'}
hist(
    RN4CAST$pa,
    main = "Histogram of Reduced Personal Accomplishment Score",
    xlab = "Reduced Personal Accomplishment Score"
)
```

The distribution of PA is skewed, with only very few high values. 

## Multilevel Poisson model using runjags

`runjags` only works with complete data, so we first delete the missing values in personal accomplishment.

```{r missing}
RN4CAST_complete <- RN4CAST[!is.na(RN4CAST$pa), ] # Delete missing values in pa
```

This is where the best part comes in: the `template.jags` function in the `rjags` package. We can use the syntax of `lme4` to specify our mixed model, and then `template.jags` writes all the jags code *for* us! For example, to get the jags syntax for a mixed effects model predicting reduced personal accomplishment, with a fixed intercept, a random intercept for unit, and a random intercept for hospital, we run the chunk below.  

```{r scale}
RN4CAST_complete$beds <- c(scale(RN4CAST_complete$beds))
RN4CAST_complete$we <- c(scale(RN4CAST_complete$we))
RN4CAST_complete$expe <- c(scale(RN4CAST_complete$expe))
```

```{r template0, message = FALSE, warning=FALSE}
# ?template.jags #run this for more information on the default settings
template_model0 <- template.jags(
    # lme4 syntax for a MEM predicting pa from a random intercept unit + hospital
    formula = pa ~ (1 | unit) + (1 | hosp) + tech + teach + beds + unitsur + we + expe + full,
    # specify data source
    data = RN4CAST_complete,
    # specify output file name for the template
    file = "JAGSmodel0.txt",
    # specify Poisson model
    family = "poisson",
    # specify whether you want to write all observations to the template
    write.data = FALSE
)
```

This creates a file for you, called `JAGSmodel0.txt`, in your current directory.
Check it out!
In it, we are given the complete `jags` syntax for a Poisson mixed effects model.
You can run `?template.jags` to see the defaults of the function.
Specifically, right now we set a $\text{Gamma}(0.001, .001)$ prior on the precision of the two random intercepts and a vague $\text{Normal}(0,10^{-6})$ prior on the fixed effects (in this case, a fixed intercept only). Another default is the number of chains (2), which we can always change.

In the first part of the assignment, we're asked to run exactly this model, but instead we have to test what prior to put on the precision of the random intercepts: an inverse gamma or a uniform. In this case, let's say I want to set a $\text{Uniform}(0.001,100)$ prior (I'm just picking something randomly from one of the dissertation papers; this is something we still need to change, of course).
Then, we run the following chunk to get the syntax for this model:

```{r template-uniform, message=FALSE, warning=FALSE}
model0_unif <- template.jags(
    formula = pa ~ (1 | unit) + (1 | hosp) + tech + teach + beds + unitsur + we + expe + full,
    data = RN4CAST_complete,
    file = "JAGSmodel0_unif.txt",
    # we have to decide here: what would be a good range for the uniform prior?
    # any examples in class?
    precision.prior = "dunif(0.001, 100)", # make an informed decision later
    family = "poisson",
    write.data = FALSE,
    n.chains = detectCores() # make an informed decision later
)
```

You can check out the created syntax to make sure it looks good, but another great thing about `runjags`: we can now just run the model directly from `R` without needing to manually copy/paste anything!
For this, we use the `run.jags` function to run the model we just specified our syntax for.
Run `?run.jags` to get more information about the defaults of the function.

```{r run-mod}
# ?run.jags #run this for more information on the default settings
JAGS.mod_uniform <- run.jags(
    # specify the syntax file
    model0_unif,
    # specify the data source (only necessary when write.data = FALSE)
    data = RN4CAST_complete,
    monitor = c(
        "intercept", "unit_precision", "hosp_precision", "beds_coefficient",
        "we_coefficient",
        "expe_coefficient",
        "tech_effect",
        "teach_effect",
        "unitsur_effect",
        "full_effect", "deviance"
    ),
    burnin = 4000, # make informed decision later (choosing speed here)
    sample = 10000, # make informed decision later (choosing speed here)
    method = "rjparallel"
)
dic <- extract(JAGS.mod_uniform, what = "dic")
# ped <- extract(JAGS.mod_uniform, what = "ped")
```

Et voila! The model ran, and we can inspect its results. 

```{r summary-mod}
summary(JAGS.mod_uniform)
```

## Visualization

We can also visualize all the results easily. The different plot types are `plot.type = c("trace", "ecdf", "histogram", "autocorr", "crosscorr")`.
You can also specify for which variable you want the plot.
The different options are `vars = c("intercept", "unit_precision", "hosp_precision", "deviance", "resid.sum.sq")`.
You can read up more about `runjags` in the documentation here: <https://cran.r-project.org/web/packages/runjags/runjags.pdf>. 

```{r plot-function}
# Convenience function for plotting
plot_jags <- function(type, var) {
    plot(JAGS.mod_uniform, plot.type = type, vars = var)
}
```

For example, here are all possible plots for the precision of the random intercept for unit:

```{r plots, message=FALSE, out.width="50%", fig.align='center'}
plot_jags("trace", "unit_precision")
plot_jags("ecdf", "unit_precision")
plot_jags("histogram", "unit_precision")
plot_jags("autocorr", "unit_precision")
plot_jags("crosscorr", NA)
```

Our next steps are now the following:

- Everyone should ideally try to read the documentation of `runjags` by the next meeting, so we know what we can and can't do
- Everyone tries to get this set-up and run some models (ideally, the ones asked for)
- We have to choose the parameters (range) of the uniform prior for the precision
- We'll make an informed decision on the number of chains (`n.chains`) specified in `template.jags`
- We'll make an informed decision on the number of burnin iterations and samples

Again, please take a look at the documentation [here](https://cran.r-project.org/web/packages/runjags/runjags.pdf) and/or let us know if you find something else that's helpful. It would be great if we could all run some models before the next meeting :-D.

```{r}
plot(JAGS.mod_uniform, layout = c(9, 4))
```